%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight} 
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{Imran}{Karim}
\position{Environmental Scientist{\enskip\cdotp\enskip}Project Manager}
\address{Lahore, Pakistan}

\mobile{(+92) 323-0531104}
\email{imrankareemi07@gmail.com}
\linkedin{imran-karim-env} % Placeholder - Update with actual ID

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Imran Karim~~~·~~~CV}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%-------------------------------------------------------------------------------

% --- SUMMARY ---
\cvsection{Summary}
\begin{cvparagraph}
Detail-oriented Environmental Scientist and Project Manager with a strong foundation in EIA/IEE reporting, sustainable development, and corporate operations. Proven track record in managing mega-scale environmental projects and conducting baseline surveys for international development initiatives, including ADB-funded projects. Co-Founder of a youth-led NGO with demonstrated leadership in stakeholder engagement, business development, and strategic communication.
\end{cvparagraph}


% --- EXPERIENCE ---
\cvsection{Experience}
\begin{cventries}

% Job 1
  \cventry
    {Assistant Project Manager} % Job title
    {Eco Syntec Consulting Services} % Organization
    {Lahore, Pakistan} % Location
    {Sep. 2025 - Present} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinate operations for mega-scale environmental projects, ensuring strict compliance with EPA sustainability standards and timely delivery of technical reports.}
        \item {Spearhead business development initiatives; draft technical proposals and contracts to secure new contracts and expand client portfolios.}
        \item {Design high-impact presentations for public hearings and stakeholder consultations to enhance brand visibility and community buy-in.}
        \item {Oversee internal workflows, manage recruitment support, and lead team coordination efforts to optimize project lifecycles.}
      \end{cvitems}
    }

% Job 2
  \cventry
    {Environmental Specialist Intern} % Job title
    {Eco Syntec Consulting Services} % Organization
    {Lahore, Pakistan} % Location
    {Aug. 2025 - Sep. 2025} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Authored detailed environmental assessment reports (IEE/EIA) for senior consultants.}
        \item {Successfully organized and facilitated official public hearings and stakeholder consultations regarding environmental impact.}
        \item {Conducted initial market research and content creation to support firm marketing strategies.}
      \end{cvitems}
    }

% Job 3
  \cventry
    {Field Officer / Project Intern} % Job title
    {Sustainability Through Environmental Professional Services (STEPS)} % Organization
    {Punjab, Pakistan} % Location
    {Feb. 2025 - Mar. 2025} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted critical baseline data collection for an \textbf{Asian Development Bank (ADB)} funded Transmission Line Project (Faisalabad to Islamabad).}
        \item {Assessed environmental conditions and gathered socio-economic data to determine project impacts on local rehabilitation.}
        \item {Deployed technical survey skills to ensure accurate data logging for the project's Environmental Impact Assessment (EIA).}
      \end{cvitems}
    }

% Job 4
  \cventry
    {Co-Founder} % Job title
    {ACT Org Pakistan} % Organization
    {Lahore, Pakistan} % Location
    {Nov. 2022 - Present} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a student-led NGO focused on climate change awareness and environmental activism in underprivileged schools across Pakistan.}
        \item {Partner with diverse organizations to execute educational campaigns regarding climate threats and sustainability.}
      \end{cvitems}
    }

\end{cventries}


% --- EDUCATION ---
\cvsection{Education}
\begin{cventries}

  \cventry
    {Bachelors in Environmental Sciences (Grade: A)} % Degree
    {Government College University (GCU)} % Institution
    {Lahore, Pakistan} % Location
    {2021 - 2025} % Date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Coordinator, Environmental Protection Society.}
        \item {Focus on Thesis and Scientific Writing.}
      \end{cvitems}
    }

  \cventry
    {Summer School, Environmental Science} % Degree
    {National University of Sciences and Technology (NUST)} % Institution
    {Islamabad, Pakistan} % Location
    {Aug. 2025} % Date
    {
    }

\end{cventries}


% --- SKILLS ---
\cvsection{Skills}
\begin{cvskills}

  \cvskill
    {Environmental Tech} % Category
    {EIA/IEE Reporting, ArcGIS, Circular Economy, Waste Management, Sustainability Standards} % Skills

  \cvskill
    {Data \& Software} % Category
    {SPSS, MS Office (Advanced Excel), Graphic Design Tools, Technical Writing} % Skills

  \cvskill
    {Project Management} % Category
    {Business Development, Proposal Writing, Stakeholder Management, HR Coordination} % Skills

  \cvskill
    {Languages} % Category
    {English (Professional), Urdu (Native)} % Skills

\end{cvskills}


% --- CERTIFICATIONS ---
\cvsection{Certifications \& Trainings}
\begin{cvhonors}

  \cvhonor
    {Certified Peer Reviewer} % Award/Cert
    {Elsevier Researcher Academy (Manuscript Review \& Figure Design)} % Event/Org
    {Online} % Location
    {Nov. 2024} % Date

  \cvhonor
    {Circular Economy} % Award/Cert
    {Sustainable Materials Management (Ghent University / Lund University)} % Event/Org
    {Online} % Location
    {May 2024} % Date

  \cvhonor
    {Solid Waste Mgmt.} % Award/Cert
    {Municipal Solid Waste Management in Developing Countries (EPFL)} % Event/Org
    {Online} % Location
    {May 2024} % Date

  \cvhonor
    {Faecal Sludge Mgmt.} % Award/Cert
    {Introduction to Faecal Sludge Management (EPFL)} % Event/Org
    {Online} % Location
    {May 2024} % Date

\end{cvhonors}


%-------------------------------------------------------------------------------
\end{document}