%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant Project Manager} % Job title
    {Eco Syntec Consulting Services} % Organization
    {Lahore, Pakistan} % Location
    {Sep. 2025 - Present} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinate operations for mega-scale environmental projects, ensuring strict compliance with EPA sustainability standards and timely delivery of technical reports.}
        \item {Spearhead business development initiatives; draft technical proposals and contracts to secure new contracts and expand client portfolios.}
        \item {Design high-impact presentations for public hearings and stakeholder consultations to enhance brand visibility and community buy-in.}
        \item {Oversee internal workflows, manage recruitment support, and lead team coordination efforts to optimize project lifecycles.}
      \end{cvitems}
    }
  \vspace{4.0mm} % Added explicit buffer for pixel-perfect spacing

%---------------------------------------------------------
  \cventry
    {Environmental Specialist Intern} % Job title
    {Eco Syntec Consulting Services} % Organization
    {Lahore, Pakistan} % Location
    {Aug. 2025 - Sep. 2025} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Authored detailed environmental assessment reports (IEE/EIA) for senior consultants.}
        \item {Successfully organized and facilitated official public hearings and stakeholder consultations regarding environmental impact.}
        \item {Conducted initial market research and content creation to support firm marketing strategies.}
      \end{cvitems}
    }
  \vspace{4.0mm}

%---------------------------------------------------------
  \cventry
    {Field Officer / Project Intern} % Job title
    {STEPS (Sustainability Through Env. Professional Services)} % Organization
    {Punjab, Pakistan} % Location
    {Feb. 2025 - Mar. 2025} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted critical baseline data collection for an \textbf{Asian Development Bank (ADB)} funded Transmission Line Project (Faisalabad to Islamabad).}
        \item {Assessed environmental conditions and gathered socio-economic data to determine project impacts on local rehabilitation.}
        \item {Deployed technical survey skills to ensure accurate data logging for the project's Environmental Impact Assessment (EIA).}
      \end{cvitems}
    }
  \vspace{4.0mm}

%---------------------------------------------------------
  \cventry
    {Co-Founder} % Job title
    {ACT Org Pakistan} % Organization
    {Lahore, Pakistan} % Location
    {Nov. 2022 - Present} % Date
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a student-led NGO focused on climate change awareness and environmental activism in underprivileged schools across Pakistan.}
        \item {Partner with diverse organizations to execute educational campaigns regarding climate threats and sustainability.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}